%%%%
% MTecknology's Resume
%%%%
% Author: Michael Lustfield
% License: CC-BY-4
% - https://creativecommons.org/licenses/by/4.0/legalcode.txt
%%%%

\documentclass[letterpaper,10pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%
%% BEGIN_FILE: mteck.sty
%% NOTE: Everything between here and END_FILE can
%% be relocated to "mteck.sty" and then included with:
%\usepackage{mteck}

% Dependencies
% NOTE: Some packages (lastpage, hyperref) require second build!
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{lastpage}
\usepackage{hyperref}
% Sans-Serif
%\usepackage[sfdefault]{FiraSans}
%\usepackage[sfdefault]{roboto}
%\usepackage[sfdefault]{noto-sans}
%\usepackage[default]{sourcesanspro}

% Serif
\usepackage{CormorantGaramond}
\usepackage{charter}

% Colors
% Use with \color{Name}
% Can wrap entire heading with {\color{accent} [...] }
\usepackage{xcolor}
\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

% Misc. Options
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

% Adjust Margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright

% ATS Readability
\input{glyphtounicode}
\pdfgentounicode=1

%-----------------%
% Custom Commands %
%-----------------%

% Centered title along with subtitle between HR
% Usage: \documentTitle{Name}{Details}
\newcommand{\documentTitle}[2]{
  \begin{center}
    {\Huge\scshape\color{accentTitle} #1}
    \vspace{10pt}
    {\color{accentLine} \hrule}
    \vspace{2pt}
    %{\footnotesize\color{accentTitle} #2}
    \footnotesize{#2}
    \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}

% Create a footer with correct padding
% Usage: \documentFooter{\thepage of X}
\newcommand{\documentFooter}[1]{
  \setlength{\footskip}{10.25pt}
  \fancyfoot[C]{\footnotesize #1}
}

% Simple wrapper to set up page numbering
% Usage: \numberedPages
% WARNING: Must run pdflatex twice!
\newcommand{\numberedPages}{
  \documentFooter{\thepage/\pageref{LastPage}}
}

% Section heading with horizontal rule
% Usage: \section{Title}
\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \scshape\raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

% Section heading with separator and content on same line
% Usage: \tinysection{Title}
\newcommand{\tinysection}[1]{
  \phantomsection
  \addcontentsline{toc}{section}{#1}
  {\scshape\large{\bfseries\color{accentText}#1} {\color{accentLine} |}}
}

% Indented line with arguments left/right aligned in document
% Usage: \heading{Left}{Right}
\newcommand{\heading}[2]{
  \hspace{10pt}#1\hfill#2\\
}

% Adds \textbf to \heading
\newcommand{\headingBf}[2]{
  \heading{\textbf{#1}}{\textbf{#2}}
}

% Adds \textit to \heading
\newcommand{\headingIt}[2]{
  \heading{\textit{#1}}{\textit{#2}}
}

% Template for itemized lists
% Usage: \begin{resume_list} [items] \end{resume_list}
\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=30pt]
}{
  \end{itemize}
  %\vspace{-2pt}
}

% Formats an item to use as an itemized title
% Usage: \itemTitle{Title}
\newcommand{\itemTitle}[1]{
  \item[] \underline{#1}\vspace{4pt}
}

% Bullets used in itemized lists
\renewcommand\labelitemi{--}

%% END_FILE: mteck.sty
%%%%%%%%%%%%%%%%%%%%%%


%===================%
% John Doe's Resume %
%===================%

%\numberedPages % NOTE: lastpage requires a second build
%\documentFooter{\thepage of 2} % Does similar without using lastpage
\begin{document}

  %---------%
  % Heading %
  %---------%

  \documentTitle{Nghiem Thi Hang}{
    % Web Version
    %\raisebox{-0.05\height} \faPhone\ [redacted - web copy] ~
    %\raisebox{-0.15\height} \faEnvelope\ [redacted - web copy] ~
    %%
    Saitama, Japan \\
    \href{tel:07085191501}{
      \raisebox{-0.05\height} \faPhone\ 070-8519-1501} ~
    \href{mailto:nghiemthihang89@gmail.com}{
      \raisebox{-0.15\height} \faEnvelope\ nghiemthihang89@gmail.com} \\
    \vspace{2pt}
    \href{https://hangnghiem.github.io/nghiemhang/}{
      \raisebox{-0.15\height}{\color{accentText} \faGlobe\ \underline{hangnghiem.github.io/nghiemhang}}} ~
    \href{https://github.com/hangnghiem}{
      \raisebox{-0.15\height}{\color{accentText} \faGithub\ \underline{github.com/hangnghiem}}} ~
    \href{https://www.linkedin.com/in/hang-nghiem-045871a4/}{
      \raisebox{-0.15\height}{\color{accentText} \faLinkedin\ \underline{linkedin.com/in/hang-nghiem}}}
  }

  %---------%
  % Summary %
  %---------%

  \tinysection{Summary}
  Natural Language Processing (NLP) professional with 7 years of experience in linguistic data, prompt engineering, and AI model evaluation. Skilled in programming (Python, JavaScript, React) and AI engineering, having built full-stack web applications.

  %--------%
  % Skills %
  %--------%

  \section{Skills}
    \begin{resume_list}
      \item \textbf{Programming \& Tools:} Python, JavaScript, HTML/CSS, Git.
      \item \textbf{AI / LLM Engineering:} Prompt Engineering, LLM Evaluation, Model Output QA.
      \item \textbf{Analytical:} Error Analysis, Factuality Checking, Edge-Case Identification, Auditing, Data-Quality Standards.
      \item \textbf{Linguistic:} Semantic \& Pragmatic Analysis, Annotation, Localization, Cultural Relevance.
      \item \textbf{Languages:} Vietnamese (native), English (business), Japanese (intermediate).
    \end{resume_list}

  %----------%
  % Projects %
  %----------%

  \section{Projects}
  \vspace{3pt}
  {\footnotesize\textit{AI-assisted builds --- demos \& source on \href{https://hangnghiem.github.io/nghiemhang/}{portfolio} and \href{https://github.com/hangnghiem}{GitHub}.}}\\
  \vspace{-3pt}
  \begin{resume_list}
    \item \textbf{AI Daily News} \,--\, AI news turned into leveled English lessons with audio and quizzes. \textit{(React, Web Speech API)}
    \item \textbf{LocalGPT} \,--\, ChatGPT-style chat app with streaming, running locally via Ollama. \textit{(React, Ollama / OpenAI API)}
    \item \textbf{Fairy Tale Kingdom Builder} \,--\, Gamified English-learning app for kids. \textit{(React, Zustand)}
    \item \textbf{TimeTrack} \,--\, Activity tracker with charts and JSON export/import. \textit{(JavaScript, Chart.js)}
  \end{resume_list}

  %------------%
  % Experience %
  %------------%

  \section{Recent Experience}

  \headingBf{Cognizant Japan}{Jan 2025 -- Present}
  \headingIt{Vietnamese Language Expert, supporting Google}{}
  \begin{resume_list}
  
  \itemTitle{Project: Generative AI}
    \item {Curate, audit, and validate high-fidelity ``golden datasets'' used as ground truth for supervised fine-tuning (SFT) and model alignment.}
    \item {Assess model reasoning, accuracy, and safety to identify capability and performance gaps.}
    \item {Execute Side-by-Side (SxS) evaluations to benchmark performance across models, versions, and human writers.}
    \item {Test newly deployed features and synthesize insights to guide engineering and product teams.}
    
  \end{resume_list}
  
  \headingBf{Aceolution Japan}{Jan 2024 -- Dec 2024}
  \headingIt{Linguistic Project Manager}{}
  \begin{resume_list}

  \itemTitle{Project: Generative AI, NLP}
        \item {Review, and evaluate natural language data.}
        \item {Localize prompts, and review AI model responses.}
        \item {Maintain, and improve the quality of NLP systems.}
        \item {Evaluate, update, and contribute to guideline development.}
        \item {Manage team work, and monitor team performance.}
  \end{resume_list}

  \headingBf{Adecco Group, Japan}{Dec 2018 -- Dec 2023}
  \headingIt{Vietnamese Associate Linguist, supporting Google}{}
  \begin{resume_list}
   
    \itemTitle{Project: NLP}
    \item {Review, annotate linguistic data, and develop grammar.} 
        \item {Identify, and address gaps in annotation.}
        \item {Contribute to Speech and Text-to-Speech improvement, text normalization of named entities, and localization.}
  \end{resume_list}

  \headingBf{Phuong Dong University, Vietnam}{Aug 2012 -- Jun 2014}
  \headingIt{English Teacher}{}
  \begin{resume_list}
   
    \item {Plan, design, and organize comprehensive instructional materials and lesson plans.} 
        \item {Evaluate student progress, and learning outcomes.}
        \item {Conduct researches on student learning to improve the quality of teaching and learning.}
  \end{resume_list}
  %-----------%
  % Education %
  %-----------%

  \section{Education}
 \begin{resume_list}
 \item {\textbf{MA - English:} }{Vietnam National University, Hanoi, Vietnam, Sep 2012 --  Jun 2014.}\\
 \item {\textbf{BA - English:} }{Vietnam National University, Hanoi, Vietnam, Sep 2007 --  Jun 2011.}  
\end{resume_list}


  %----------------------------%
  % Extracurricular Activities %
  %----------------------------%
 

\end{document}