%%%%
% MTecknology's Resume
%%%%
% Author: Michael Lustfield
% License: CC-BY-4
% - https://creativecommons.org/licenses/by/4.0/legalcode.txt
%%%%

\documentclass[letterpaper,10pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%
%% BEGIN_FILE: mteck.sty
%% NOTE: Everything between here and END_FILE can
%% be relocated to "mteck.sty" and then included with:
%\usepackage{mteck}

% Dependencies
% NOTE: Some packages (lastpage, hyperref) require second build!
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{lastpage}
\usepackage{hyperref}
% Sans-Serif
%\usepackage[sfdefault]{FiraSans}
%\usepackage[sfdefault]{roboto}
%\usepackage[sfdefault]{noto-sans}
%\usepackage[default]{sourcesanspro}

% Serif
\usepackage{CormorantGaramond}
\usepackage{charter}

% Colors
% Use with \color{Name}
% Can wrap entire heading with {\color{accent} [...] }
\usepackage{xcolor}
\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

% Misc. Options
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

% Adjust Margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright

% ATS Readability
\input{glyphtounicode}
\pdfgentounicode=1

%-----------------%
% Custom Commands %
%-----------------%

% Centered title along with subtitle between HR
% Usage: \documentTitle{Name}{Details}
\newcommand{\documentTitle}[2]{
  \begin{center}
    {\Huge\scshape\color{accentTitle} #1}
    \vspace{10pt}
    {\color{accentLine} \hrule}
    \vspace{2pt}
    %{\footnotesize\color{accentTitle} #2}
    \footnotesize{#2}
    \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}

% Create a footer with correct padding
% Usage: \documentFooter{\thepage of X}
\newcommand{\documentFooter}[1]{
  \setlength{\footskip}{10.25pt}
  \fancyfoot[C]{\footnotesize #1}
}

% Simple wrapper to set up page numbering
% Usage: \numberedPages
% WARNING: Must run pdflatex twice!
\newcommand{\numberedPages}{
  \documentFooter{\thepage/\pageref{LastPage}}
}

% Section heading with horizontal rule
% Usage: \section{Title}
\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \scshape\raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

% Section heading with separator and content on same line
% Usage: \tinysection{Title}
\newcommand{\tinysection}[1]{
  \phantomsection
  \addcontentsline{toc}{section}{#1}
  {\scshape\large{\bfseries\color{accentText}#1} {\color{accentLine} |}}
}

% Indented line with arguments left/right aligned in document
% Usage: \heading{Left}{Right}
\newcommand{\heading}[2]{
  \hspace{10pt}#1\hfill#2\\
}

% Adds \textbf to \heading
\newcommand{\headingBf}[2]{
  \heading{\textbf{#1}}{\textbf{#2}}
}

% Adds \textit to \heading
\newcommand{\headingIt}[2]{
  \heading{\textit{#1}}{\textit{#2}}
}

% Template for itemized lists
% Usage: \begin{resume_list} [items] \end{resume_list}
\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=30pt]
}{
  \end{itemize}
  %\vspace{-2pt}
}

% Formats an item to use as an itemized title
% Usage: \itemTitle{Title}
\newcommand{\itemTitle}[1]{
  \item[] \underline{#1}\vspace{4pt}
}

% Bullets used in itemized lists
\renewcommand\labelitemi{--}

%% END_FILE: mteck.sty
%%%%%%%%%%%%%%%%%%%%%%


%===================%
% John Doe's Resume %
%===================%

%\numberedPages % NOTE: lastpage requires a second build
%\documentFooter{\thepage of 2} % Does similar without using lastpage
\begin{document}

  %---------%
  % Heading %
  %---------%

  \documentTitle{Nghiem Thi Hang}{
    % Web Version
    %\raisebox{-0.05\height} \faPhone\ [redacted - web copy] ~
    %\raisebox{-0.15\height} \faEnvelope\ [redacted - web copy] ~
    %%
    1-29-15-1 Komaba Urawa-ku  Saitama Japan \\
    \href{tel:08048796139}{
      \raisebox{-0.05\height} \faPhone\ 070-8519-1501} ~
    \href{mailto:nghiemthihang89@gmail.com}{
      \raisebox{-0.15\height} \faEnvelope\ nghiemthihang89@gmail.com} ~
    
  }

  %---------%
  % Summary %
  %---------%

  \tinysection{Summary}
  With 7 years in Natural Language Processing (NLP) and Generative AI, I specialize in linguistic data review, annotation, localization, and model evaluation. My expertise includes reviewing prompts and responses, evaluating model performance, refining model outputs for naturalness, and testing new features to deliver data-driven, actionable insights.

  %--------%
  % Skills %
  %--------%

  \section{Skills}
    \begin{resume_list}
      \item \textbf{Linguistic Skills:} Semantic and Pragmatic Analysis, Review and Validation, Cultural Relevance.
      \item \textbf{Writing Skills:} Rewriting, Prompt Designing, Creative Writing Skills.
      \item \textbf{Analytical and Logical Skills:} Error Analysis, Factuality Check, Scope identification, Auditing.
      \item \textbf{Technical Skills:} Google Workspace.
      \item \textbf{Languages:} Vietnamese (native), English (business), Japanese (intermediate).
    \end{resume_list}

  %------------%
  % Experience %
  %------------%

  \section{Recent Experience}

  \headingBf{Cognizant Japan}{Jan 2025 -- Present}
  \headingIt{Vietnamese Language Expert, supporting Google}{}
  \begin{resume_list}
  
  \itemTitle{Project: Generative AI}
    \item {Review, and validate high-quality "golden data" sets used for supervised AI model training.}
    \item {Evaluate model responses, and rewrite responses for accuracy and fluency.}
    \item {Execute Side-by-Side (SxS) evaluation across models, versions, and human writers.}
    \item {Conduct testing of new features, and provide insights on model performance.}
    
  \end{resume_list}
  
  \headingBf{Aceolution Japan}{Jan 2024 -- Dec 2024}
  \headingIt{Linguistic Project Manager}{}
  \begin{resume_list}

  \itemTitle{Project: Generative AI, NLP}
        \item {Review, and evaluate natural language data.}
        \item {Localize prompts, and review AI model responses.}
        \item {Maintain, and improve the quality of NLP systems.}
        \item {Evaluate, update, and contribute to guideline development.}
        \item {Manage team work, and monitor team performance.}
  \end{resume_list}

  \headingBf{Adecco Group, Japan}{Dec 2018 -- Dec 2023}
  \headingIt{Vietnamese Associate Linguist, supporting Google}{}
  \begin{resume_list}
   
    \itemTitle{Project: NLP}
    \item {Review, annotate linguistic data, and develop grammar.} 
        \item {Identify, and address gaps in annotation.}
        \item {Contribute to Speech and Text-to-Speech improvement, text normalization of named entities, and localization.}
  \end{resume_list}

  \headingBf{Phuong Dong University, Vietnam}{Aug 2012 -- Jun 2014}
  \headingIt{English Teacher}{}
  \begin{resume_list}
   
    \item {Plan, design, and organize comprehensive instructional materials and lesson plans.} 
        \item {Evaluate student progress, and learning outcomes.}
        \item {Conduct researches on student learning to improve the quality of teaching and learning.}
  \end{resume_list}
  %-----------%
  % Education %
  %-----------%

  \section{Education}
 \begin{resume_list}
 \item {\textbf{MA - English:} }{Vietnam National University, Hanoi, Vietnam, Sep 2012 --  Jun 2014.}\\
 \item {\textbf{BA - English:} }{Vietnam National University, Hanoi, Vietnam, Sep 2007 --  Jun 2011.}  
\end{resume_list}


  %----------------------------%
  % Extracurricular Activities %
  %----------------------------%
 

\end{document}